An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-30 VLDB2026/main.tex
change 4.2.2
Update main.tex

	\noindent\textbf{\underline{DSG \cite{DSG}.}}   
	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets. SeRF allows incremental insertion but requires ordered attributes. DSG introduces the first dynamic RF-ANN framework supporting data insertion with unordered attributes while maintaining efficient range filtering.
	DSG relies on two data structures: 1) A rectangle tree partitions query space into rectangular regions, each corresponding to a group of queries sharing nearest neighbors. 2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
	With these structures, only few regions need updates when inserting new data. During the query process, the system considers only edges valid for current attribute range, boosting efficiency.

@@

	\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}. \textcolor{red}{We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality}. VBASE adopts a post-filtering strategy. However, it employs an iterative filtering mechanism: during index traversal, each node is immediately checked against the WHERE clause, and non-matching nodes are discarded. This avoids the issue in PASE where the final result set may contain fewer than $k$ results.

@@

	To comprehensively assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, which includes the following 5 core metrics:

@@

	For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different Recall and QPS.

@@

	We next evaluate the query performance of AF-ANN search algorithms, focusing on 3 main scenarios.

>>>>

	\noindent\textbf{\underline{DSG \cite{DSG}.}}   
	Most RF-ANN search methods, such as iRange and WinFilter, are designed for static datasets. SeRF allows incremental insertion but requires ordered attributes. DSG introduces the first dynamic RF-ANN framework supporting data insertion with unordered attributes while maintaining efficient range filtering.
	DSG relies on two data structures: 1) A rectangle tree partitions query space into rectangular regions, each corresponding to a group of queries sharing nearest neighbors. 2) A dynamic segment graph is a neighbor graph where each edge is annotated with its valid attribute range.
	With these structures, only few regions need updates when inserting new data. \textcolor{blue}{The system considers only edges valid for current attribute range to boost efficiency during search.}

@@

	\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}. \textcolor{red}{We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality}. VBASE adopts a post-filtering strategy. However, it employs an iterative filtering mechanism: during index traversal, \textcolor{blue}{each node is checked} against the WHERE clause, and non-matching nodes are discarded. This avoids the issue in PASE where the final result set may contain fewer than $k$ results.

@@

	To assess the overall performance of different algorithms, we adopt a multi-dimensional quantitative evaluation framework~\cite{compare}, including the following 5 core metrics:

@@

	\textcolor{blue}{For all algorithms, we adopt recommended settings from the original study and adjust the parameters related to search in order to obtain different Recall and QPS.}

@@

	We next evaluate the query performance of AF-ANN search \textcolor{blue}{methods}, focusing on 3 main scenarios.
